--- 
title: "Ejemplo de Dashboard"
author: "Capacitación R Intermedio"
format:
  dashboard:
    output-file: "dashboard_example.html"
    logo: images/logo_portada2.png
    orientation: rows
--- 

# Page 1 {orientation="rows" scrolling="false"}

```{r}
library(tidyverse)
library(ggplot2)

airquality <- airquality %>% 
  mutate(
    wind_kmhr = Wind / 0.6213711922,
    temp_celsius = (Temp - 32)*5/9
  )
```

## Row {height=5%}

::: {.card}
Análisis de Calidad de Aire en la ciudad de Nueva York. Mayo a Septiembre, 1973.
Referencia: <https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/airquality>.
:::

## Row {height=35%}

```{r}
library(DT)
DT::datatable(airquality)
```

## Row {height=60% .tabset}

```{r}
#| title: Ozono versus Temperatura [°C]
ggplot(airquality, aes(temp_celsius, Ozone)) +
  geom_point() + 
  geom_smooth(method = "loess")
```

```{r}
#| title: Ozono versus Viento [km/hr]
ggplot(airquality, aes(wind_kmhr, Ozone)) +
  geom_point() + 
  geom_smooth(method = "loess")
```

```{r}
#| title: Temperatura [°C] versus Viento [km/hr]
ggplot(airquality, aes(wind_kmhr, temp_celsius)) +
  geom_point() + 
  geom_smooth(method = "loess")
```


# Page 2 {orientation="rows" scrolling="true"}

## Row {height=10%}

::: {.card}
Gapminder identifies systematic misconceptions about important global trends and proportions and uses reliable data to develop easy to understand teaching materials to rid people of their misconceptions.
Gapminder is an independent Swedish foundation with no political, religious, or economic affiliations.
Learn more about the Gampminder dataset at <https://www.gapminder.org/data/>.
:::

## Row {height=90%}

```{r}
library(gapminder)
library(DT)
DT::datatable(gapminder)
```

```{r}
#| fig-width: 10
#| fig-height: 8
paises <- c("Peru", "Bolivia", "Chile")
# etiquetas <- data.frame(nombre_paises = paises, x = c(1975, 1965, 1962), y = c(6, 7, 4))
gapminder %>% 
  filter(country %in% paises) %>% 
  ggplot() +
  aes(x = year, y = lifeExp, color = country) +
  geom_line()
```
